### 2022-06-27 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_betacov_mapping@05560fa1bb7abf6736a3912e8ae484ca2c47d35e 🚀

On closer inspection, these patterns recapitulate the evolutionary
history of both the order Chiroptera and the genus
\emph{Betacoronavirus}. Horseshoe bats (Rhinolophidae) are both the
reservoirs of the SARS-like viruses (subgenus \emph{Sarbecovirus}) and a
possible ancestral host of \emph{Betacoronavirus}.\textsuperscript{17}
The hotspots of host richness and viral diversity in southeast
Asia---both of which are disproportionately high, considering the global
landscape of bat species richness---are almost entirely driven by viral
adaptive radiation through host switching within this
clade\textsuperscript{3,14}. In contrast, the Neotropical hotspot of
viral distinctiveness is driven by isolation by host vicariance. Out of
the four main groups of betacoronaviruses, only the subgenus
\emph{Merbecovirus} (MERS-like viruses) has been found in animals in the
Americas---an introduction that is generally presumed to be
ancient.\textsuperscript{3} While comparatively understudied, New World
merbecoviruses have been found in the ghost-faced bats (Mormoopidae),
New World leaf-nosed bats (Phyllostomidae), and free-tailed bats
(Molossidae) (add cite: Olival 2020 PLoS Pathogens). The former two
groups are endemic to the Neotropics, while the explosive adaptive
radiations of the latter two (and particularly the phyllostomids) are
responsible for the hotspot of bat diversity in the Amazon. Together,
these clades of New World bats play host to a distinct regime of
betacoronavirus coevolution.

>>>>

On closer inspection, these patterns recapitulate the evolutionary
history of both the order Chiroptera and the genus
\emph{Betacoronavirus}. Horseshoe bats (Rhinolophidae) are both the
reservoirs of the SARS-like viruses (subgenus \emph{Sarbecovirus}), the
group of pandemic threats that have been of the greatest interest to
researchers\textsuperscript{17} (and so have been sampled most
intensively).\textsuperscript{16} The hotspots of host richness and
viral diversity in southeast Asia---both of which are disproportionately
high, considering the global landscape of bat species richness---are
almost entirely driven by viral adaptive radiation through host
switching within this clade\textsuperscript{3,14}. In contrast, the
Neotropical hotspot of viral distinctiveness is driven by isolation by
host vicariance. Out of the four main groups of betacoronaviruses, only
the subgenus \emph{Merbecovirus} (MERS-like viruses) has been found in
animals in the Americas---an introduction that is generally presumed to
be ancient.\textsuperscript{3} While comparatively understudied, New
World merbecoviruses have been found in the ghost-faced bats
(Mormoopidae), New World leaf-nosed bats (Phyllostomidae), and
free-tailed bats (Molossidae) (add cite: Olival 2020 PLoS Pathogens).
The former two groups are endemic to the Neotropics, while the explosive
adaptive radiations of the latter two (and particularly the
phyllostomids) are responsible for the hotspot of bat diversity in the
Amazon. Together, these clades of New World bats play host to a distinct
regime of betacoronavirus coevolution.
